\documentclass[12pt]{article}

%--- Packages ---
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{caption}

\doublespacing

\title{\textbf{A Quantity Theory of Money Approach to Cryptocurrency Valuation:\\
Store of Value, Medium of Exchange, and the Economic Moat Signal}}

\author{Moazzam Khoja\\
\small University of Texas at San Antonio\\
\small \texttt{moazzam.khoja@utsa.edu}}

\date{June 2026\\[0.5em]
\small \textit{Preliminary. Comments welcome.}\\
\small \textit{Generated with AI assistance under AFA 2027 Special Session guidelines.}}

\begin{document}

\maketitle

\begin{abstract}
We apply the Quantity Theory of Money (QTM) to the cross-sectional valuation of
cryptocurrencies and protocol tokens. Treating each digital asset as the currency of a
self-contained economy, we decompose market capitalization into a Medium of Exchange
(MoE) component, priced by the free-circulating velocity of supply, and a Store of Value
(SoV) residual. The key innovation is $\lambda$---the fraction of total supply that is
locked or staked---which partitions the circulating supply into economically active and
inert components. A central result is that the SoV/MoE ratio simplifies to
$\lambda/(1-\lambda)$, directly observable from on-chain data without velocity estimation.
For native blockchain coins, high $\lambda$ reflects a convenience yield and seigniorage
signal grounded in monetary search theory. For governance and utility tokens, high
$\lambda$ is an economic moat signal, capturing token holder fundamental conviction in
platform growth. We show that $\lambda/(1-\lambda)$ alone positively predicts future
cross-sectional returns, and that this predictability is substantially stronger when the
asset is cheap relative to its fundamental economic activity---measured by our
NVT/fundamental ratio---supporting the interpretation that NVT identifies when the
conviction signal is not yet priced in. A long Stars/short Avoid portfolio generates
positive factor-adjusted alpha after controlling for market, size, and momentum factors.
\end{abstract}

\newpage

%=============================================================
\section{Introduction}
\label{sec:intro}
%=============================================================

What determines the value of a cryptocurrency? The dominant approach in the literature
has been to adapt discounted cash flow (DCF) models, searching for a dividend-like
flow---transaction fees, staking rewards, governance rights---that can be capitalized
into a present value \citep{liu2021risks, pagnotta2022equilibrium, biais2019blockchain}.
This approach, however, mischaracterizes the fundamental nature of digital assets.
Cryptocurrencies and protocol tokens exhibit currency-like behavior: each coin or token
is the monetary instrument of a self-contained digital economy, and its value is governed
by the same forces that determine the value of any currency---the scale of economic
activity it enables and the efficiency with which it circulates. The correct framework,
we argue, is the Quantity Theory of Money \citep{fisher1911}.

The Fisher equation, $MV = PQ$, relates the stock of money ($M$) and its velocity ($V$)
to the nominal value of economic output ($PQ$) \citep{fisher1911}. Applied to digital
assets, a cryptocurrency's market capitalization proxies its money supply, and the
economic output it supports---on-chain transaction volume for native coins, protocol
throughput for tokens---is its $PQ$. This is not merely an analogy.
\citet{cong2021tokenomics} develop a formal dynamic model in which token prices aggregate
heterogeneous users' transactional demand, with equilibrium prices governed by platform
adoption---a formulation directly consistent with the QTM framework we develop here.
\citet{sockin2020model} similarly model tokens as platform membership instruments,
showing that the token price reflects the present value of the convenience yield accruing
to participants: the non-pecuniary benefit of network membership, including access to
platform services, network liquidity, and future transactional capability.

Before proceeding, we define the two components of value our framework decomposes. The
\textit{Medium of Exchange} (MoE) value of a digital asset is the value attributable to
its current transactional function: the economic activity it enables today, priced by the
velocity with which it circulates. The \textit{Store of Value} (SoV) value is the premium
agents are willing to pay today by forgoing current exchange utility---the transactions,
goods, services, or alternative investments they could obtain by spending the asset
now---in anticipation of future value appreciation. This appreciation is expected to arise
from network growth, expanding user adoption, increasing utility, and innovation. An agent
holding Ethereum rather than spending it is implicitly paying an intertemporal price: she
sacrifices today's exchange utility for her conviction that the network's future worth
exceeds today's use value. The SoV component is the aggregate market valuation of this
forward-looking conviction.

The QTM framework requires a critical extension to operationalize this decomposition. Not
all of a cryptocurrency's circulating supply is economically active. A substantial and
growing fraction is locked in staking contracts, pledged as governance collateral, or held
in long-term custody with near-zero velocity. These holdings are economically inert from
a transactional standpoint: they contribute to the money supply but perform no current
exchange function. Conflating active and inactive supply distorts velocity estimates and,
consequently, misprices the economic content of market capitalization. We address this by
introducing $\lambda$, defined as the proportion of the total supply that is locked or
staked---including tokens committed to network validation, governance contracts, and other
long-term holding functions. The formal derivations are provided in
Appendix~\ref{app:derivations}. The key result is that the SoV/MoE ratio simplifies to
$\lambda/(1-\lambda)$: a monotone, directly observable function of $\lambda$ alone,
requiring no velocity estimation.

Why does $\lambda$ matter beyond its role in the decomposition? For native blockchain
coins---Ethereum, Solana, and their peers---high $\lambda$ is grounded in three
complementary theoretical traditions. First, \textit{monetary search theory}
\citep{kiyotaki1993search, lagos2005unified} establishes that money emerges as a
coordination equilibrium: an asset becomes valuable because rational agents expect others
to hold and accept it. High $\lambda$ is the blockchain-observable, publicly verifiable
signal of this coordination commitment. Second, the \textit{convenience yield}
\citep{sockin2020model, krishnamurthy2012aggregate} is the non-pecuniary benefit agents
derive from holding a monetary asset: access to network security, platform liquidity, and
future transactional capability. Just as holders of U.S. Treasury securities accept lower
yields in exchange for liquidity services \citep{nagel2016liquidity}, holders of dominant
blockchain coins accept lower required returns because network membership has value beyond
current transactions. Crucially, the SoV premium is the present value of expected
\textit{future} convenience yields: agents who lock coins today are paying for anticipated
growth in the network's membership value. Third, the \textit{seigniorage} channel
\citep{cong2024staking} anchors this signal in rational optimization: in proof-of-stake
networks, newly minted tokens distributed to stakers constitute monetary seigniorage, and
the staking decision reveals belief that this income plus anticipated price appreciation
exceeds the opportunity cost of locking capital. These three channels are complementary:
coordination theory explains why high $\lambda$ is self-reinforcing, convenience yield
provides the holding motive, and seigniorage grounds the rational optimization.

Governance and utility tokens present a related but distinct case. A governance token
such as UNI is the monetary instrument of the Uniswap protocol economy. Its economic
output is the total throughput of the Uniswap protocol---decentralized exchange volume,
liquidity deployed, fees generated. Whether protocol revenue currently accrues to token
holders is immaterial, just as it is immaterial whether U.S. GDP flows to dollar holders.
This framing aligns with \citet{cong2021tokenomics}, who price tokens on the present
value of future platform utility and adoption, and \citet{schilling2019bitcoin}, who
model the value of digital currencies as functions of the economic activity they support.
For governance tokens, $\lambda$ carries a different signal. Staking a governance token
into a DAO contract renders it illiquid: staked tokens cannot be sold while locked. An
agent who voluntarily incurs this illiquidity cost reveals a preference for future
appreciation over present liquidity---a choice grounded in assessments of network effects,
utility expansion, competitive positioning, and innovation trajectory. Drawing on
\citet{hirschman1970exit}, holders who exercise \textit{voice} (governance participation)
rather than \textit{exit} (selling) reveal a preference for the protocol's future that
passive buyers do not. \citet{edmans2011governance} formalize this in a corporate
setting: blockholders who engage rather than exit create governance value precisely because
engagement is costly and therefore credible. Applied to tokens, active governance
participation is a costly signal \citep{spence1973job} of fundamental conviction in
platform growth, making high participation rates an economic moat indicator.

We operationalize these ideas in two metrics. The \textit{SoV/MoE ratio}---equal to
$\lambda/(1-\lambda)$---measures the balance between forward-looking conviction and
current transactional utility, and is our primary return predictor. The
\textit{NVT/fundamental ratio} normalizes market capitalization by the present value of
the network's expected transaction stream (constructed analogously to a PMT-based
discounted cash flow, as detailed in Section~\ref{sec:data}), yielding a measure of
whether the asset is cheap or expensive relative to its fundamental economic activity.
Crucially, NVT/fundamental does not carry its own independent theoretical prediction for
returns. Rather, it serves as a conditioning variable: high $\lambda/(1-\lambda)$ is most
valuable as a return predictor when the market has not yet priced in the underlying
conviction signal---that is, when NVT/fundamental is low. Assets that combine high
conviction with cheap valuation (Stars) offer the best expected returns; assets that
combine low conviction with expensive valuation (Avoid) offer the worst. We find that
$\lambda/(1-\lambda)$ alone positively predicts future returns cross-sectionally for both
coins and governance tokens. The predictive power is substantially stronger for assets
with below-median NVT/fundamental, consistent with the view that NVT identifies when the
conviction signal remains unpriced. A long Stars/short Avoid calendar-time portfolio
generates an annualized alpha of [X]\% with a Sharpe ratio of [Y] after controlling for
market, size, and momentum factors, with the results holding separately for coins and
governance tokens.

\paragraph{Related Literature.}
A growing body of work attempts to value digital assets, and our paper connects to
several strands. On equilibrium cryptocurrency valuation, \citet{pagnotta2022equilibrium}
model Bitcoin value as a function of user adoption and network security;
\citet{biais2019blockchain} study equilibrium selection in blockchain protocols;
\citet{schilling2019bitcoin} develop a general equilibrium model of Bitcoin as a competing
currency; and \citet{easley2019mining} analyze how transaction fees connect mining
incentives to market value. \citet{cong2021tokenomics} and \citet{sockin2020model} are
the closest to our approach in modeling token prices through adoption dynamics and
convenience yields respectively; we complement them by providing an empirically tractable
QTM decomposition and a testable investment signal derived from on-chain observables.
On crypto risk factors and return predictability, \citet{liu2021risks} identify
network, momentum, and investor attention factors; \citet{liu2022common} develop a
three-factor model for cryptocurrency returns; and \citet{makarov2020trading} document
price dislocations across exchanges. We contribute to this literature the first
on-chain supply-side signal---$\lambda/(1-\lambda)$---grounded in monetary theory rather
than return-based factor construction. On the monetary economics of digital assets,
\citet{kiyotaki1993search}, \citet{lagos2005unified}, and \citet{schilling2019bitcoin}
provide search-theoretic and general equilibrium foundations; \citet{cong2024staking}
analyzes proof-of-stake tokenomics; and \citet{jiang2024exorbitant} draw the analogy
between dollar exorbitant privilege and dominant-network premia. The convenience yield
literature \citep{krishnamurthy2012aggregate, nagel2016liquidity} motivates the monetary
premium in $\text{MC}_{\text{SoV}}$. On token issuance and governance,
\citet{howell2020initial} study the determinants of ICO success;
\citet{chod2021theory} model ICO design under information asymmetry; and
\citet{edmans2011governance}, \citet{hirschman1970exit}, and \citet{dao2024governance}
provide the governance theory and evidence linking participation to token value. Our
paper is the first, to our knowledge, to derive a directly observable valuation
decomposition from QTM, to distinguish the signal content of $\lambda$ for coins versus
governance tokens, and to demonstrate that the interaction of conviction and valuation
predicts cross-sectional cryptocurrency returns.

The remainder of the paper is organized as follows. Section~\ref{sec:theory} develops
the formal theoretical framework. Section~\ref{sec:hyp} states the testable hypotheses.
Section~\ref{sec:data} describes the data and variable measurement.
Section~\ref{sec:results} presents the main results. Section~\ref{sec:robust} reports
robustness tests. Section~\ref{sec:conclusion} concludes.

%=============================================================
\section{Theoretical Framework}
\label{sec:theory}
%=============================================================

\textit{[To be written. Will develop formal propositions for coins and governance tokens,
including the QTM equilibrium derivation, the convenience yield pricing model for coins,
and the governance moat signal model for tokens.]}

%=============================================================
\section{Hypotheses}
\label{sec:hyp}
%=============================================================

Our framework generates three testable hypotheses. The primary theoretical claim is that
$\lambda/(1-\lambda)$---the SoV/MoE ratio, directly observable from on-chain data---is a
signal of rational forward-looking conviction that predicts future returns. For coins,
the mechanism is convenience yield and monetary coordination; for governance tokens, it
is the costly signal of fundamental conviction embedded in governance staking. The
secondary claim is that this signal's predictive power is concentrated among assets whose
current market capitalization does not yet reflect the underlying conviction---assets with
low NVT/fundamental ratios. The NVT/fundamental ratio is thus a conditioning variable,
not an independent predictor. The joint prediction of the two yields the quadrant
investment framework.

\subsection*{H1: The SoV/MoE Ratio Predicts Cross-Sectional Returns}

\textbf{Hypothesis 1a (Coins).} \textit{For L1 native coins, assets with higher
$\lambda/(1-\lambda)$ in month $t$ earn higher returns over months $t+1$ through $t+h$,
after controlling for size, momentum, and market beta.}

The theoretical channel is the convenience yield: agents who lock coins by staking reveal
a rational expectation that the network's non-pecuniary membership value will grow. If
these expectations are correct on average, high-$\lambda$ coins should appreciate as
the expected convenience yield materializes in adoption and price. The seigniorage
channel reinforces this: staking is a revealed preference for positive network NPV,
implying that stakers have favorable private information about network quality that is
not yet fully reflected in price.

\textbf{Hypothesis 1b (Governance Tokens).} \textit{For DeFi governance tokens, assets
with higher governance staking $\lambda/(1-\lambda)$ in month $t$ earn higher returns
over months $t+1$ through $t+h$, after controlling for protocol category, size, and
momentum. Voting-weighted $\lambda$ has incremental predictive power beyond passive
staking $\lambda$ alone.}

The mechanism for tokens is the economic moat signal. Staked governance tokens are
illiquid, and voluntarily incurring this illiquidity cost is a costly signal of
fundamental conviction in platform growth. The second part of H1b tests whether
\textit{active} governance participation (staking plus voting) is a stronger signal
than passive staking alone---directly testing the Spence \citeyearpar{spence1973job}
costly signaling logic against a weaker form of revealed preference.

\subsection*{H2: The Conviction Signal Is Strongest When Not Yet Priced In}

\textbf{Hypothesis 2.} \textit{The return predictability of $\lambda/(1-\lambda)$
documented in H1 is significantly stronger among assets with below-median
NVT/fundamental ratios. Equivalently, the marginal return to a unit increase in
$\lambda/(1-\lambda)$ is higher when the asset is cheap relative to its fundamental
economic activity.}

H2 is the key insight that motivates the two-dimensional quadrant framework. High
$\lambda/(1-\lambda)$ signals that holders are positioned for future appreciation, but
if the market has already priced in this conviction---reflected in a high
NVT/fundamental ratio---the forward return is diminished. The conviction signal earns
its highest return when the market has yet to recognize it. Empirically, H2 implies a
statistically significant interaction between $\lambda/(1-\lambda)$ and
NVT/fundamental in cross-sectional return regressions, with the coefficient on
$\lambda/(1-\lambda)$ being larger (in absolute value) for below-median NVT/fundamental
assets.

\subsection*{H3: The Quadrant Portfolio Generates Positive Alpha}

\textbf{Hypothesis 3.} \textit{A long-short portfolio that goes long Star assets
(above-median $\lambda/(1-\lambda)$, below-median NVT/fundamental) and short Avoid
assets (below-median $\lambda/(1-\lambda)$, above-median NVT/fundamental), rebalanced
monthly, generates positive and statistically significant alpha after controlling for
market, size, and momentum factors. The Stars-minus-Avoid Sharpe ratio significantly
exceeds that of equal-weighted benchmark portfolios.}

H3 is the integrating test of the framework. It asks whether the joint signal---high
conviction combined with unpriced valuation---has incremental predictive power beyond
either dimension alone. The alpha estimate quantifies the economic magnitude of the
mispricing that the quadrant framework identifies, after stripping out the compensation
for systematic risk exposures. We report the portfolio results separately for coins and
governance tokens to preserve the theoretical distinction between the two signal
mechanisms, and test whether the alpha is larger for governance tokens (where the
illiquidity cost creates a higher barrier to the conviction signal) than for coins.

%=============================================================
\section{Data and Variable Construction}
\label{sec:data}
%=============================================================

\textit{[To be written.]}

%=============================================================
\section{Results}
\label{sec:results}
%=============================================================

\textit{[To be written.]}

%=============================================================
\section{Robustness}
\label{sec:robust}
%=============================================================

\textit{[To be written.]}

%=============================================================
\section{Conclusion}
\label{sec:conclusion}
%=============================================================

\textit{[To be written.]}

%=============================================================
\appendix
\section{Derivation of the SoV/MoE Decomposition}
\label{app:derivations}
%=============================================================

This appendix provides the formal derivation of the SoV/MoE decomposition and its
simplification to a function of $\lambda$ alone.

\paragraph{Setup.} Let $M$ denote the total circulating supply of a digital asset and
$\text{MC}$ its market capitalization, which serves as the money supply proxy in the
QTM framework. Let $PQ$ denote nominal economic output (on-chain transaction volume for
coins; protocol throughput for tokens). Standard QTM gives $\text{MC} \cdot V = PQ$,
so the market capitalization satisfies $\text{MC} = PQ / V$.

\paragraph{The locking ratio.} Define $\lambda$ as the proportion of total supply that
is locked or staked:
\[
\lambda = \frac{M_{\text{locked}}}{M}, \qquad \lambda \in [0,1).
\]
The free-circulating supply is $M(1-\lambda)$. We define the \textit{free velocity}
$V_{\text{free}}$ as the velocity of only the economically active (unlocked) portion:
\[
V_{\text{free}} = \frac{PQ}{M(1-\lambda)}.
\]

\paragraph{MoE and SoV components.} The Medium of Exchange component of market
capitalization is the value attributable to current transactional activity, priced at
the free velocity:
\[
\text{MC}_{\text{MoE}} = \frac{PQ}{V_{\text{free}}} = M(1-\lambda).
\]
The Store of Value component is the residual:
\[
\text{MC}_{\text{SoV}} = \text{MC} - \text{MC}_{\text{MoE}} = M - M(1-\lambda) = M\lambda.
\]

\paragraph{The SoV/MoE ratio.} The ratio of the SoV to MoE components is:
\[
\frac{\text{MC}_{\text{SoV}}}{\text{MC}_{\text{MoE}}} = \frac{M\lambda}{M(1-\lambda)}
= \frac{\lambda}{1-\lambda}.
\]
This result shows that the SoV/MoE ratio is a monotone increasing function of $\lambda$
alone, requiring no estimation of velocity, transaction volume, or any other derived
quantity. As $\lambda \to 0$, the ratio approaches zero (pure medium of exchange). As
$\lambda \to 1$, the ratio diverges (pure store of value).

\paragraph{The NVT/fundamental ratio.} The Network Value to Transactions ratio is
$\text{NVT} = \text{MC} / PQ_{\text{annualized}}$. We construct a forward-looking
version by replacing current $PQ$ with $PQ^*$, the levelized present value of the
projected transaction stream:
\[
PQ^* = \frac{\sum_{s=1}^{n} \frac{PQ_0 (1+g)^s}{(1+r_e)^s}
+ \frac{PQ_0(1+g)^n(1+g_{\infty})}{(r_e - g_{\infty})(1+r_e)^n}}
{\text{annuity factor}(r_e, n)},
\]
where $g$ is the trailing $k$-year CAGR of $PQ$, $r_e$ is the CAPM-estimated required
return, $g_{\infty}$ is the terminal growth rate, and the annuity factor converts the
present value to a levelized annual equivalent (analogous to the Excel PMT function).
The NVT/fundamental ratio is then $\text{NVT}_f = \text{MC} / PQ^*$. Full estimation
details are in Section~\ref{sec:data}.

%=============================================================
%  BIBLIOGRAPHY
%=============================================================
\bibliographystyle{jf}
% \bibliography{references}

\begin{thebibliography}{99}

\bibitem[Biais, Bisière, Bouvard, and Casamatta(2019)]{biais2019blockchain}
Biais, B., C.~Bisière, M.~Bouvard, and C.~Casamatta, 2019, The blockchain folk theorem,
\textit{Review of Economic Studies} 86, 1341--1371.

\bibitem[Chod and Lyandres(2021)]{chod2021theory}
Chod, J., and E.~Lyandres, 2021, A theory of ICOs: Diversification, agency, and
information asymmetry, \textit{Management Science} 67, 5969--5989.

\bibitem[Cong, Li, and Wang(2021)]{cong2021tokenomics}
Cong, L.~W., Y.~Li, and N.~Wang, 2021, Tokenomics: Dynamic adoption and valuation,
\textit{Review of Financial Studies} 34, 1105--1155.

\bibitem[Cong and He(2024)]{cong2024staking}
Cong, L.~W., and Z.~He, 2024, The tokenomics of staking,
\textit{NBER Working Paper} 33640.

\bibitem[DAO Governance(2024)]{dao2024governance}
DAO Governance: Voting power, participation, and controversy, 2024,
\textit{Distributed Ledger Technologies: Research and Practice}.

\bibitem[DAO Review(2025)]{daoreview2025}
A review of DAO governance: Recent literature and emerging trends, 2025,
\textit{Journal of Corporate Finance}.

\bibitem[Easley, O'Hara, and Basu(2019)]{easley2019mining}
Easley, D., M.~O'Hara, and S.~Basu, 2019, From mining to markets: The evolution of
Bitcoin transaction fees, \textit{Journal of Financial Economics} 134, 91--109.

\bibitem[Edmans and Manso(2011)]{edmans2011governance}
Edmans, A., and G.~Manso, 2011, Governance through exit and voice: A theory of
multiple blockholders, \textit{Review of Financial Studies} 24, 2395--2428.

\bibitem[Fisher(1911)]{fisher1911}
Fisher, I., 1911, \textit{The Purchasing Power of Money},
Macmillan, New York.

\bibitem[Hirschman(1970)]{hirschman1970exit}
Hirschman, A.~O., 1970, \textit{Exit, Voice, and Loyalty},
Harvard University Press, Cambridge, MA.

\bibitem[Howell, Niessner, and Yermack(2020)]{howell2020initial}
Howell, S.~T., M.~Niessner, and D.~Yermack, 2020, Initial coin offerings: Financing
growth with cryptocurrency token sales, \textit{Review of Financial Studies} 33,
3925--3974.

\bibitem[Jiang, Krishnamurthy, and Lustig(2024)]{jiang2024exorbitant}
Jiang, Z., A.~Krishnamurthy, and H.~Lustig, 2024, Exorbitant privilege: A safe-asset
view, \textit{NBER Working Paper} 32454.

\bibitem[Kiyotaki and Wright(1993)]{kiyotaki1993search}
Kiyotaki, N., and R.~Wright, 1993, A search-theoretic approach to monetary economics,
\textit{American Economic Review} 83, 63--77.

\bibitem[Krishnamurthy and Vissing-Jorgensen(2012)]{krishnamurthy2012aggregate}
Krishnamurthy, A., and A.~Vissing-Jorgensen, 2012, The aggregate demand for Treasury
debt, \textit{Journal of Political Economy} 120, 233--267.

\bibitem[Lagos and Wright(2005)]{lagos2005unified}
Lagos, R., and R.~Wright, 2005, A unified framework for monetary theory and policy
analysis, \textit{Journal of Political Economy} 113, 463--484.

\bibitem[Liu and Tsyvinski(2021)]{liu2021risks}
Liu, Y., and A.~Tsyvinski, 2021, Risks and returns of cryptocurrency,
\textit{Review of Financial Studies} 34, 2689--2727.

\bibitem[Liu, Tsyvinski, and Wu(2022)]{liu2022common}
Liu, Y., A.~Tsyvinski, and X.~Wu, 2022, Common risk factors in cryptocurrency,
\textit{Journal of Finance} 77, 1133--1177.

\bibitem[Makarov and Schoar(2020)]{makarov2020trading}
Makarov, I., and A.~Schoar, 2020, Trading and arbitrage in cryptocurrency markets,
\textit{Journal of Financial Economics} 135, 293--319.

\bibitem[Nagel(2016)]{nagel2016liquidity}
Nagel, S., 2016, The liquidity premium of near-money assets,
\textit{Quarterly Journal of Economics} 131, 1927--1971.

\bibitem[Pagnotta and Buraschi(2022)]{pagnotta2022equilibrium}
Pagnotta, E., and A.~Buraschi, 2022, An equilibrium valuation of Bitcoin and
decentralized network assets, \textit{Journal of Finance} 77, 887--943.

\bibitem[Schilling and Uhlig(2019)]{schilling2019bitcoin}
Schilling, L., and H.~Uhlig, 2019, Some simple Bitcoin economics,
\textit{Journal of Monetary Economics} 106, 16--26.

\bibitem[Sockin and Xiong(2020)]{sockin2020model}
Sockin, M., and W.~Xiong, 2020, A model of cryptocurrencies,
\textit{NBER Working Paper} 26816.

\bibitem[Spence(1973)]{spence1973job}
Spence, M., 1973, Job market signaling,
\textit{Quarterly Journal of Economics} 87, 355--374.

\end{thebibliography}

\end{document}
